\thesistitle

### 2019-07-16 sections/clonerefactor.tex
Changed removeall to make it more clean

\begin{equation}\label{eq:removeall}
\text{For each new clone }C_{new}\text{ found, remove all clones in }(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
\end{equation}

@@

\begin{equation}\label{eq:removeexisting}
(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) \neq \emptyset \Rightarrow S = S \cup C_{new}
\end{equation}

>>>>

\begin{equation}\label{eq:removeall}
S = S \setminus (C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
\end{equation}

@@

\begin{equation}\label{eq:removeexisting}
(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) = \emptyset \Rightarrow S = S \cup C_{new}
\end{equation}
